BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-15 Msc-Slides/main.tex
Fixed DBI slide again

A dynamic binary analysis
technique in which the behaviour of an application is inspected at run-time via the
injection of analysis code. 
\bigskip
\begin{block}{}
\begin{lstlisting}[basicstyle=\ttfamily\large,xleftmargin=50pt]
<@\textcolor{red}{record(libcall, arg1)}@> 
retval = libcall(arg1, &arg2)
<@\textcolor{red}{record(retval, *arg2)}@> 
\end{lstlisting}
\end{block}
\bigskip
\bigskip
\textbf{Problem 1}: existing products have limited logging capabilites

>>>>

A dynamic binary analysis
technique in which the behaviour of an application is inspected at run-time via the
injection of analysis code. 
\bigskip
\begin{block}{}
\begin{lstlisting}[basicstyle=\ttfamily\large,xleftmargin=50pt]
<@\textcolor{red}{record\_before(libcall\_name, arg1)}@> 
retval = libcall(arg1, &arg2)
<@\textcolor{red}{record\_after(retval, *arg2)}@> 
\end{lstlisting}
\end{block}
\bigskip
\bigskip
\textbf{Problem 1}: existing products have limited logging capabilites
